Proposal to improve BBC Search through the use of Linked Data

### 2014-05-16 chapter3.1.tex
Almost finished chapter 4.
More headway with Chapter 5, improved how word counts are done and change RDF graph diagrams to render the DOT via dot2text to make scaling nicer rather than going via PNG.

\subsection{Current Implementation}

@@

\begin{sidewaysfigure}
  \begin{center}
    \includegraphics[width=\linewidth]{question-time.png}
  \end{center}
  \caption{Semantic metadata found within \emph{Question Time} home page}
  \label{question-time}
\end{sidewaysfigure}

@@

\begin{sidewaysfigure}
  \begin{center}
    \includegraphics[width=\linewidth]{politics.png}
  \end{center}
  \caption{Semantic metadata around the \emph{Politics} programme genre}
  \label{politics}
\end{sidewaysfigure}

Returning to the semantic view of Question Time in figure~\ref{question-time},
we can see that the page also describes further entities representing
a \emph{episodes} with identifiers \texttt{bbcprog:b006t1q9\#programme}
and \texttt{bbcprog:b04446v3\#programmes}. There are a far greater
number of episodes linked, but the illustration here is reduced to
just the two for brevity.

@@

\begin{sidewaysfigure}
  \begin{center}
    \includegraphics[width=\linewidth]{keepod.png}
  \end{center}
  \caption{Metadata found within a BBC News article page}
  \label{keepod}
\end{sidewaysfigure}

@@

\begin{sidewaysfigure}
  \begin{center}
    \includegraphics[width=\linewidth]{keepod-tagged.png}
  \end{center}
  \caption{BBC News article page's metadata enriched using DBPedia Spotlight}
  \label{keepod-tagged}
\end{sidewaysfigure}

>>>>

\subsection{Current Implementation}
\label{sec:current-impl}

@@

\begin{sidewaysfigure}
  \begin{center}
    \begin{dot2tex}[dot,pgf,scale=0.25]
      \input{question-time.dot}
    \end{dot2tex}
  \end{center}
  \caption{Semantic metadata found within \emph{Question Time} home page}
  \label{question-time}
\end{sidewaysfigure}

@@

\begin{sidewaysfigure}
  \begin{center}
    \begin{dot2tex}[dot,pgf,scale=0.41]
      \input{politics.dot}
    \end{dot2tex}
  \end{center}
  \caption{Semantic metadata around the \emph{Politics} programme genre}
  \label{politics}
\end{sidewaysfigure}

Returning to the semantic view of Question Time in figure~\ref{question-time},
we can see that the page also describes another entity representing
an episode \emph{episodes} with identifier \texttt{bbcprog:b006t1q9\#programme}.
There are a far greater
number of episodes linked, but the illustration here is reduced to
just the two for brevity.

@@

\begin{sidewaysfigure}
  \begin{center}
    \begin{dot2tex}[dot,pgf,scale=0.41]
      \input{keepod.dot}
    \end{dot2tex}
  \end{center}
  \caption{Metadata found within a BBC News article page}
  \label{keepod}
\end{sidewaysfigure}

@@

\begin{sidewaysfigure}
  \begin{center}
    \begin{dot2tex}[dot,pgf,scale=0.41]
      \input{keepod-tagged.dot}
    \end{dot2tex}
  \end{center}
  \caption{BBC News article page's metadata enriched using DBPedia Spotlight}
  \label{keepod-tagged}
\end{sidewaysfigure}

### 2014-05-16 chapter5.3.tex
More headway with Chapter 5, improved how word counts are done and change RDF graph diagrams to render the DOT via dot2text to make scaling nicer rather than going via PNG.

@@

@@

>>>>

\begin{figure}
  \begin{center}
    \begin{dot2tex}[dot,pgf,scale=0.41]
      \input{basic-ontology.dot}
    \end{dot2tex}
  \end{center}
  \caption{Basic ontology modelling the traditional ``title, link, description'' search result}
  \label{fig:initial-ontology}
\end{figure}

@@

The ``Results Page'' subteam can thus focus on initiating
several iterations of user experience design, user testing
and development of the results page and it is expected this
feature will continue to develop in the background as
other features are worked on by other subteams. It is likely
individual stories might add to the domain model even
to make this simple, responsive rebuild of the results page.

The front end application can continue to search the
existing search indexes independant of any work being done
to improve the ingest chain. The importance of developing
this feature first is to ensure the information architecture
and domain models are defined up front. After this point,
the other subteams can proceed with the features below
while the results page developers keep iterating on
a user interaction that evolves through user testing and
feedback.

@@

The ``Ingest'' subteam needs to ensure the Ingest API can
accept content meeting the basic vocabulary outline in
figure~\ref{fig:initial-onotologu}, validating ones
that do not contain the basic fields and evolve the API. If
the results page developers choose to alter the domain
model based on design iterations and user feedback, then
these changes can propogate back as requirements for the
content ingest.

The team should also evaluate any relevant technologies for the
search indexes and ensure they are searchable by the
developers working on the results page.

Elasticsearch is a standalone search server based on Apache Lucene
that can store, index and retrieve schemaless JSON structures.
The indexing chain is to deal with RDF graphs, for which JSON-LD
is a powerful JSON serialisation that can be sent to Elasticsearch
without any transformation.
A simple prototype of an ingest function written in Python
that receives JSON-LD is shown in listing~\ref{lst:ingest}.

\begin{lstlisting}[language=Python]
from elasticsearch import Elasticsearch
import json

def ingest_jsonld(jsonld_string):
  body = {'jsonld': json.loads(jsonld_string)}
  ElasticSearch().index(index='search', body=body, doc_type='item')
\label{lst:ingest}
\end{lstlisting}

The focus for the ingest work should then be around setting
up mappings in Elasticsearch (if the prototype proves promising)
to arrange indexes to enable sensible retrieval behaviour.
